\textsf{Are large language models superhuman chemists?}

### 2024-10-31 src/tex/appendix.tex
add per-topic performance table
Former-commit-id: 3ea98c52c9a66c89e3190485c1a18c39c5c8a91f

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_FINAL_SKILL_flat.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_FINAL_SKILL_flat.png}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

@@

\begin{table}
    \caption{\textbf{Performance of the models on the \chembench corpus.} The table shows the fraction of questions answered correctly by the models for different topics. Models with \enquote{T-one} in the name were run for a temperature of 1, which allows us to study the temperature effect in the benchmark. Systems with \enquote{ReAct} in the name are tool augmented, i.e., they can call external tools such as web search or a calculator to answer the questions better. However, we limit those systems to ten calls to the \gls{llm}. This constraint often led the systems to not find the correct answer within the specified number of calls. In this case, we consider the answer as incorrect (see \Cref{sec:react-environment}).}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_topic_table.tex}
    }
    \label{tab:performance_table_topic}
\end{table}

\begin{table}
    \caption{\textbf{Performance of the models on \chembenchmini.} The table shows the fraction of questions answered correctly by the models for different topics.}
    \resizebox{\textwidth}{!}{
    \variable{output/performance_topic_table_human_subset.tex}
    }
    \label{tab:performance_table_human_subset_topic}
\end{table}
